Literature Review

### 2018-07-10 LiteratureReview/LiteratureReview3000.tex
updated intro LR3k

@@

Those who are diagnosed with dementia suffer from a number of cogniive, emotional and behavioural problems. In terms of cognitive problems, they suffer from deficiencies to memory, planning and organising, speech and language, visuo-spatial tasks and difficulties in orienting in time and place. From an emotional perspective, those with dementia can suffer from mental health problems such as depression, anxiety and irritability.  \newline

>>>>

Alzheimer's Disease (AD) is a neurodegenerative disease in which the hallmark clinical symptoms are cognitive deficits such as problems with episodic and semantic memory, organising and planning, difficulties with language and visuospatial deficits. In addition, these symptoms are often accompanied by emotional difficulties such as depression and irritability and behavioural difficulties. \newline

@@

Current thinking suggests that the cognitive deficits associated with AD often begin before the clinical symptoms of the disease become apparent. \newline
